### 2023-12-18 latex/Plusone_configs/paper.tex
Light GBM

>>>>

\subsubsection*{2.2 LightGBM}
LightGBM (Light Gradient Boosting Machine) is an algorithmic framework for Gradient Boosting Decision Trees (GBDT) proposed by Guolin Ke et al. (2017). It supports efficient parallel computation and boasts advantages such as faster training speed and lower memory consumption.

It primarily incorporates two algorithmic improvements: Gradient-based One-Side Sampling (GOSS) and Exclusive Feature Bundling (EFB).

GOSS retains instances with large gradients and performs random sampling on instances with small gradients. It then adjusts the new sampling with weight adjustment to ensure that the information gain remains unchanged. This approach allows for the calculation of information gain using only the remaining data with high gradients. Compared to XGBoost, which traverses all feature values, this method \ref{Gradient-based One-Side Sampling} saves a considerable amount of time and space costs.
\begin{algorithm}
	\renewcommand{\algorithmicrequire}{\textbf{Input:}}
	\renewcommand{\algorithmicensure}{\textbf{Output:}}
	\caption{Gradient-based One-Side Sampling}
	\label{Gradient-based One-Side Sampling}
	\begin{algorithmic}
        \REQUIRE $I$: training data, $d$: iterations
        \REQUIRE $a$: sampling ratio of large gradient data
        \REQUIRE $b$: sampling ratio of small gradient data
        \REQUIRE $loss$: loss function, $L$: weak learner
        \STATE $models \gets {}, fact \gets \frac{1-a}{b}$
        \STATE $topN \gets a{\times}len(I), randN \gets b{\times}len(I)$
        \FOR {$i=1 \to d$}
        \STATE $preds \gets models.predict(I)$
        \STATE $g \gets loss(I, preds), \omega \gets EqualWeight$
        \STATE $sorted \gets GetSortedIndices(abs(g))$
        \STATE $topSet \gets sorted[1:topN]$
        \STATE $randSet \gets RandomPick(sorted[topN:len(I)], randN)$
        \STATE $usedSet \gets topSet + randSet$
        \STATE $\omega[randSet] \times= fact$
        \STATE $newModel \gets L(I[usedSet], g[usedSet], \omega[usedSet])$
        \STATE $models.append(newModel)$
        \ENDFOR
	\end{algorithmic}
\end{algorithm}
High-dimensional data are usually mutually exclusive. EFB can safely bundle exclusive features into a single feature by designed feature scanning algorithm \ref{Merge Exclusive Features}.
\begin{algorithm}
	\renewcommand{\algorithmicrequire}{\textbf{Input:}}
	\renewcommand{\algorithmicensure}{\textbf{Output:}}
	\caption{Merge Exclusive Features}
	\label{Merge Exclusive Features}
	\begin{algorithmic}
        \REQUIRE $numData$: number of data
        \REQUIRE $F$: One bundle of exclusive features
        \STATE $binRanges \gets {0}, totalBin \gets 0$
        \FOR{$f \gets F$}
        \STATE $totalBin += f.numBin$
        \STATE $binRanges.append(totalBin)$
        \ENDFOR
        \FOR{$i=1 \to numData$}
        \STATE $newBin[i] \gets 0$
        \FOR{$j=1 \to len(F)$}
        \IF{$F[j].bin[i] \neq 0$}
        \STATE $newBin[i] \gets F[j].bin[i] + binRanges[j]$
        \ENDIF
        \ENDFOR
        \ENDFOR
        \ENSURE newBing, binRanges
	\end{algorithmic}
\end{algorithm}
